Paper_analyses

### 2021-09-04 Figures.Rmd
done plots - to do
match the pca tsne colos to the colors of JASP

>>>>

p$graphstyle_tsne <-  theme(#base plot theme

  # axis lines
  # axis.line.y = element_line(color="black", size = 1.5),
  # axis.line.x = element_line(color="black", size = 1,5),

  # panel
  panel.grid.major = element_blank(),
   panel.border = element_rect(colour = "black", fill=NA, size=5),
  panel.background = element_blank(),
  # panel.background = element_rect(fill="transparent"),
  # panel.border = element_rect(fill="black"),
  # strip shades (reco rectagles)
   # strip.background = element_blank(),

pca_res <- prcomp(clustering_agg[,c(20,24,25)], center = TRUE, scale. = TRUE)
plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg$y_kmeans)
stat_el
# plot_data$
plots_paper$PCA_clust <- ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels, fill = labels)) +
  geom_point(size = 2, alpha = .6)+
  geom_text(aes(label= clustering_agg$stimDescription), alpha = .4)+
  stat_ellipse(aes(fill = labels))+
  ylab("Componet 2")+
  xlab("Component 1")+
  p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+

theme(axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=3)
  )

ggsave("PCA_clust.tiff", plots_paper$PCA_clust , device = "tiff", width = 10, height = 7, dpi = 800)

### 2021-09-04 Paper_Analyses_subj_obje_arousal.Rmd
done plots - to do
match the pca tsne colos to the colors of JASP

@@

ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels)) +
  geom_point()+
  geom_text(aes(label= clustering_agg$stimDescription))

>>>>

test$Distances
```

@@

# plot_data$
ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels, fill = labels)) +
  geom_point(size = 2, alpha = .4)+
  geom_text(aes(label= clustering_agg$stimDescription))+
  stat_ellipse()+
  ylab("Componet 2")+
  xlab("Component 1")+
  p$graphstyle+
  theme()
```
